First look at Spacetime

### 2019-10-28 Output/error_reduction_analysis.tex
wrote some stuff

\section*{Computational cost}
Looking at computation time, we measure the time it takes to perform a single
application of the system matrix, not taking into account the setup cost (like
computing $\Sigma$ and $\Theta$). Figure~\ref{fig:linearity} paints a slightly
less enthousiastic picture, but it is obvious that we need more data points
before concluding anything.\todo{BV: meten we nou per DoF, of per dimensie?}
\begin{figure}[h!]
  \includegraphics[width=0.8\linewidth]{error_reduction_linearity.pdf}
  \caption{Top: time (s) per apply; bottom: time (ms) per apply per DoF.}
  \label{fig:linearity}
\end{figure}

>>>>

\section*{Computational cost}
Let's measure the time it takes to perform a single application of the system
matrix. We do not take into account the setup cost (like
computing $\Sigma$ and $\Theta$). Figure~\ref{fig:linearity} paints a slightly
demotivating picture, in that the bottom graph is not constant. We do have to
place an asterisk here: for small systems, the produced numbers are averaged over
a small number of iterations, so they change a lot from run to run.
\begin{figure}[h!]
  \includegraphics[width=0.8\linewidth]{error_reduction_linearity.pdf}
  \caption{Top: time (s) per apply; bottom: time (ms) per apply per DoF.}
  \label{fig:linearity}
\end{figure}

\section*{The solver}
As mentioned before, we use MINRES with default parameters (tolerance $10^{-5}$,
initial guess $x_0$ equal to the RHS $b$). In Figure~\ref{fig:minres}, we show
the residual norm $\|M x_k - b\|_2$ as a function of $k$ for a selection of solves.
\begin{figure}[h!]
  \includegraphics[width=0.495\linewidth]{error_reduction_minres_history_semilogy.pdf}
  \includegraphics[width=0.495\linewidth]{error_reduction_minres_history_loglog.pdf}
  \caption{Left: semi-log-y MINRES convergence graph for some solves. Right: Same results in log-log format.}
  \label{fig:minres}
\end{figure}
We see that the number of iterations increases strongly, suggesting that we could
definitely use a good preconditioner.
